\section{Coding Strategy}

The previous section defined the case-level research design. This section
describes how the main outcome is measured. The coding strategy begins from a
simple premise: official exit language is evidence about regulatory status, not
by itself evidence that a government financing function disappeared. For each
platform, I therefore code both the formal event and the post-event location of
the relevant function.

\subsection{Source hierarchy}

The source hierarchy begins with government documents, finance-bureau notices,
state-owned asset supervision documents, exchange disclosures, and company
announcements when they are available. These sources are most useful for
identifying official exit, market-oriented transformation, asset transfer, debt
replacement, restructuring, and liquidation. Bond prospectuses, credit rating
reports, legal opinions, annual reports, and audited financial statements are
often more informative about continuing public-project functions, repayment
arrangements, fiscal support, issuer guarantees, related-party transfers, and
changes in the role of the company after exit. Credible financial news and
company profiles serve as supplementary sources. These materials can help
locate events and identify entities, but they do not by themselves determine
the final label.

This hierarchy matters because the most authoritative source for the formal
event is not always the most informative source for the post-event function. A
government notice may state that a platform exited a list, while a later
prospectus may show that the same issuer still carries out infrastructure
investment, entrusted construction, land preparation, or project repayment on
behalf of the local state. Conversely, a prospectus may contain
no-government-financing language, while the underlying fiscal-substitution
arrangement appears only in a debt-replacement announcement or a municipal
budget document. The coding rule therefore treats each source as evidence for
a specific component of the case rather than as a global statement about the
whole outcome.

\subsection{Condensed codebook}

The full coding protocol is maintained in the project codebook. The condensed
rule used in the paper begins by identifying the baseline platform function.
Relevant functions include infrastructure investment and financing,
land development, government-entrusted construction, policy-driven housing or
urban renewal, public utility construction, and repayment arrangements tied to
local fiscal resources. The next step is to identify the formal event, such as
exit from a financing-platform list, a no-government-financing statement,
market-oriented transformation, merger, asset transfer, debt replacement, debt
restructuring, deregistration, liquidation, or dissolution. The final coding
decision turns on the post-event location of the function. The same issuer may
continue the function, the function may move into formal fiscal channels, the
function may move to another local state-owned entity, or the original legal
entity may terminate.

A case enters the final label file only if it satisfies two requirements. It
must contain a formal event, and it must contain post-event evidence about the
relevant function. Cases with only a corporate profile, only a news summary,
only an official slogan of market-oriented transformation, or only
post-event public project evidence without a formal event are retained as
candidates rather than final labels. Purely commercial SOEs, central SOEs, and
provincial entities without a city-platform role are excluded unless the source
packet shows a platform-like local financing function.

\begin{table}[htbp]
\centering
\footnotesize
\setlength{\tabcolsep}{4pt}
\begin{tabular}{@{}>{\raggedright\arraybackslash}p{0.18\textwidth}>{\raggedright\arraybackslash}p{0.36\textwidth}>{\raggedright\arraybackslash}p{0.34\textwidth}@{}}
\toprule
Label & Positive rule & Exclusion rule \\
\midrule
Substantive exit & The formal event is followed by evidence that the issuer no
longer performs government financing or quasi-fiscal financing functions. Former
public projects may continue only if the financing has moved into budgetary
channels, special-purpose bonds, or fee-based project management. & Do not code
substantive exit from no-government-financing language alone. Continuing fiscal
repayment, entrusted construction financing, land preparation financing, or
public project financing rules it out. \\
Nominal exit & The same issuer has formal exit or compliance language but
continues the relevant platform function after the event. Evidence may include
infrastructure financing, land preparation, shantytown redevelopment, fiscal
receivables, government purchase service, project repurchase, or fiscal
subsidies. & Do not code nominal exit when the function clearly moved to a
different local state-owned entity, or when post-event sources show only
fee-based project management funded through formal fiscal channels. \\
Functional transfer & The original issuer exits, reduces its role, merges, or
is reorganized, while the relevant financing, construction, debt-management, or
public project function moves to another local state-owned entity, subsidiary,
merged group, or newly created platform. & Do not code functional transfer if
the same issuer continues the function. Do not code it when the function is
absorbed into formal fiscal channels rather than another platform-like entity.
\\
Liquidation & The firm is dissolved, deregistered, liquidated, bankrupted, or
otherwise terminated, with no evidence that the same legal entity continues
platform functions. & If a successor local SOE takes over the fiscal function,
code functional transfer and record the liquidation as part of the transfer
process. \\
\bottomrule
\end{tabular}
\caption{Condensed codebook for LGFV exit types}
\label{tab:condensed-codebook}
\end{table}

Several edge cases matter for the classification. Fee-based project management
after exit is not automatically nominal exit. If the project is funded through
formal fiscal channels and the issuer receives only a management fee, the case
is closer to substantive exit. If the issuer carries project financing,
government repayment exposure, or fiscal receivables, the case is closer to
nominal exit. Debt replacement also has two meanings. It supports substantive
exit only when legacy obligations move into formal fiscal management and no
new quasi-fiscal function is visible. If debt replacement coexists with
continued platform financing, the case remains nominal exit. Mergers and state
capital operation companies require special care. If a public financing
function is preserved inside a reorganized local SOE system, the case is coded
as functional transfer rather than substantive exit.

Each final label is accompanied by three scores. The confidence score records
whether the final label is high, medium, or low confidence. High confidence
requires a directly documented formal event, clear post-event function
evidence or rich negative evidence, and no plausible alternative label. Medium
confidence permits a partial source packet or a credible but weaker
alternative interpretation. Low confidence cases do not enter the final label
file. The source coverage score ranges from 0 to 4 and measures whether the
case has original or near-original sources for both the formal event and the
post-event function. The continued-function evidence score also ranges from 0
to 4 and measures the strength of evidence that platform-like functions
continued after the event. A high continued-function score does not
mechanically imply nominal exit because the continued function may be located
in a successor entity rather than the same issuer.

Table~\ref{tab:pilot_cases} summarizes five illustrative human-validated pilot
cases. The full label file now contains eighty validated labels; this
table is not an empirical result or an exhaustive case list. Its purpose is to
show how the same coding rule operates across different documentary patterns.

\begin{table}[htbp]
\centering
\footnotesize
\setlength{\tabcolsep}{4pt}
\begin{tabular}{@{}>{\raggedright\arraybackslash}p{0.18\textwidth}>{\raggedright\arraybackslash}p{0.22\textwidth}>{\raggedright\arraybackslash}p{0.34\textwidth}>{\raggedright\arraybackslash}p{0.13\textwidth}@{}}
\toprule
Case & Source basis & Key evidence & Final label \\
\midrule
Xi'an Hi-tech Holding & 2020 and 2026 bond prospectuses, rating report, and
supplementary financial news & The issuer reports a 2012 exit from the
financing-platform list, while later documents continue to describe
infrastructure investment, BT, entrusted-construction, and government-linked
project repayment. & Nominal exit \\
Chengdu City Construction Investment Management & 2023 bond prospectus and
Shanghai Clearing disclosure page & The issuer states that it does not
undertake government financing functions after 2015, while the same prospectus
describes continuing infrastructure investment, fiscal payment arrangements,
self-funded and financed project construction, and local debt replacement. &
Nominal exit \\
Guangzhou City Construction Investment & 2018 tracking rating report, 2018
debt-replacement announcement, and 2026 bond prospectus & The company reports
that it stopped new government-project investment and financing after 2014,
shifted to fiscal-funded entrusted management, and had part of a 2014 MTN
included in the fiscal budget for debt replacement. & Substantive exit \\
Hangzhou City Investment & 2024 bond prospectus and issuer rating report &
Qiantou Group was folded into Hangzhou City Investment, Hangzhou City
Investment succeeded Qiantou debt instruments, and Anju Group was created as a
housing-security investment, construction, and operation platform. &
Functional transfer \\
Zhuzhou State-owned Assets Investment Holding & 2026 bond prospectus and legal
opinion & The issuer reports a March 2013 exit from local government financing
platform management, while the same source set describes land preparation,
major project construction, government-entrusted work, fiscal settlement,
subsidies, and local government support. & Nominal exit \\
\bottomrule
\end{tabular}
\caption{Pilot coding examples}
\label{tab:pilot_cases}
\end{table}

These cases illustrate distinctions that are central to the measurement
strategy. Formal compliance language must be separated from functional
evidence. A prospectus may state that new debt does not constitute local
government debt, while other sections describe continuing public project
obligations. Chengdu makes this distinction especially clear because the
no-government-financing statement appears in the same document as evidence of
self-funded and financed infrastructure construction with fiscal payment
arrangements. Continuing public project management is also not always evidence
of nominal exit. In Guangzhou, the relevant distinction is that government
projects were funded through municipal fiscal funds and the company received a
management fee, rather than using the platform as an off-budget financing arm.
Functional transfer, finally, is not merely a name change. In Hangzhou, the
classification rests on equity transfer, debt succession, and the creation of a
specialized housing-security group within a reorganized municipal platform
system.

\subsection{LLM-assisted labeling}

Large language models are used to produce preliminary labels from the same
codebook and source excerpts. They do not assign final labels. The purpose of
using LLMs is to make the source review more scalable and to force each case to
be evaluated under a common decision rule. The model prompt asks for a proposed
label, a confidence level, a short rationale, the exact pieces of evidence used
for the classification, and the most plausible alternative label. The prompt
also requires the model to return \texttt{unclear} when the source packet lacks
a formal event or lacks evidence about the post-event function.

The Codex screening pass follows this rule conservatively. It keeps the
eighty human-validated labels as gold-standard observations and applies the codebook
only to pending candidates. The current pass screens 173 pending disclosures, produces
59 surrogate disclosure-level labels, and leaves 114 cases unresolved. The
surrogate labels are nominal-exit cases. They contain direct
no-government-financing language together with continuing evidence of urban
infrastructure, entrusted construction, land development, fiscal support, or
public-project functions. They correspond to 38 unique issuers because several
labels come from repeated bond disclosures for the same platform. The
statistical analysis will therefore aggregate or deduplicate them at the issuer
or city-platform level. Thirty-one issuers exactly match issuers that
already appear in the gold-standard label file under different case IDs. These
overlaps are treated as consistency checks rather than new observations. Seven
non-overlap issuers remain in the current human-validation queue. Four
packets are boundary-reviewed and excluded from the city-platform gold-standard
frame because they are province-level or specialized infrastructure SOEs rather
than core city-platform cases. The unresolved cases are not negative
outcomes. They either lack source-packet text or lack direct
formal exit or compliance evidence. This is a feature of the design rather than
a failure of automation: the model is allowed to identify source gaps instead
of guessing institutional outcomes from titles or generic disclosure language.

Human validation compares the model's evidence claims with the original
documents and removes claims that are not supported by the source text. It also
evaluates whether the model has confused legal compliance language with
functional change. This error is especially likely in bond prospectuses because
issuers often state that new debt is not local government debt while also
describing public-project obligations and fiscal payment arrangements. The
human-validated label file records the final label, alternative label,
confidence level, source coverage score, key evidence, and remaining caveat.
The final dataset is therefore not a set of model outputs. It is a set of
human-reviewed case labels whose preliminary coding was assisted by LLMs.

\subsection{Validation protocol}

The scaled dataset will be built in two layers. The first layer is a candidate
pool of at least 200 LLM-coded city-platform cases. A case enters this pool
only after the source packet identifies the company, city, source type, source
date, baseline platform function, formal event, and post-event functional
evidence when such evidence is available. The second layer is a
human-validated sample of at least 50 cases. These cases form the gold-standard
label file used to evaluate measurement quality, estimate LLM error, and
support the supervised-learning correction described in the empirical section.

The validation sample is drawn before the final outcome analysis. I first take
a random sample from the LLM-coded candidate pool. I then add a stratified
oversample of cases from low historical-capacity cities and high-debt cities.
The stratification is necessary because measurement errors are unlikely to be
evenly distributed. Low-capacity and high-debt localities often have weaker
source coverage, more debt-resolution language, and more ambiguous relations
between formal compliance and continuing platform functions. If these cases
were left to proportional sampling alone, the validation sample would be most
precise for the easiest documents and least informative for the cases where
measurement risk is highest. The sampling probabilities are recorded so that
the validation design can later be used in design-based adjustment rather than
treated as an informal audit.

Human validation follows pre-registered coding rules. Before cases are opened,
the codebook freezes the inclusion rules, exclusion rules, exit-type
definitions, edge-case rules, and scoring scales. Any later change to the
rules must be versioned and applied either to all relevant cases or to none of
them. Validators review original documents rather than model summaries. For
each case, they record the formal event, baseline platform function,
post-event function, final label, most plausible alternative label, confidence
score, source coverage score, continued-function evidence score, key source
references, and remaining caveat. Low-confidence cases remain in the candidate
file and do not enter the gold-standard label file.

Inter-coder agreement is assessed on an overlapping validation subset. Two
coders independently label the same cases using the frozen codebook. Agreement
is calculated for the four-category exit type and for the binary distinction
between substantive exit and non-substantive outcomes. Disagreements are not
resolved by majority vote. They are adjudicated by returning to the original
documents and recording which part of the rule produced the conflict: formal
event, post-event function, related-entity scope, source hierarchy, or
edge-case treatment. This procedure turns disagreement into information about
where the codebook is fragile.

The source coverage score is part of the validation protocol rather than a
descriptive afterthought. A score of 0 means that no usable original or
near-original source is available. A score of 1 covers either the formal event
or the post-event function, but not both. A score of 2 covers both elements
with limited source type, date range, or issuer scope. A score of 3 requires
multiple source types and at least one original or near-original document. A
score of 4 requires a rich source packet with clear dates, issuer scope, and
references for both the formal event and the post-event function. The final
analysis can therefore report not only the distribution of exit types, but also
the quality of the evidence supporting those labels.

The audit trail is part of the measurement contribution. Each final label is
linked to a case identifier, document identifiers, source types, line
references where available, model rationales, human rationale, alternative
label, ambiguity note, and source coverage score. This structure makes it
possible to revise a label when new documents are found without changing the
codebook. It also makes disagreement informative. When an LLM proposes
substantive exit because a prospectus contains compliance language, while human
review identifies continuing government-entrusted construction in the same
document, the disagreement identifies exactly the distinction the paper seeks
to measure.

Candidate cases are kept separate from final labels. Luzhou Xinglu is a useful
near-miss case. The source packet strongly rejects a substantive-exit
interpretation: it shows infrastructure investment-financing,
government-entrusted construction, fiscal receivables, project repayment, and
government support across 2015, 2017, 2018, 2021, and 2023. The case
nevertheless remains outside the final label table because the project has not
found a direct platform-list exit source. Zunyi Daoqiao is treated similarly.
Its documents strongly indicate continuing platform status and debt-resolution
pressure, including a rating notice that places the company inside Guizhou's
government-financing-platform debt-resolution pilot, but the case remains
outside the final label table until a direct formal-exit or
no-government-financing source is collected.
