\section{Conclusion}

This paper has argued that LGFV exit should be studied as an institutional
outcome rather than as a binary regulatory event. Official exit language
records a change in formal status, but it does not by itself show whether a
government financing function disappeared, remained with the same issuer, moved
to another local state-owned entity, or ended through liquidation. The main
task is therefore to distinguish official exit from the post-event location of
the function that made the platform politically and fiscally important.

The distinction has implications for how we understand local fiscal
formalization in China. The exit reform is commonly framed as a debt-management
policy, but its institutional content is broader. It asks local governments to
move functions once carried by quasi-fiscal platforms into more formal fiscal,
budgetary, and state-asset channels. This is the process I have called formal
fiscal substitution. Where this substitution is feasible, official exit can
become substantive exit. Where it is not feasible, local governments may comply
with central rules in form while preserving the old financing function through
nominal exit or functional transfer.

The paper's historical argument follows from this institutional problem.
Historically stronger localities are not expected to exit LGFVs simply because
they are richer today. They are expected to do so because historical
administrative and fiscal capacity may have left contemporary local states with
more routinized fiscal administration, better project preparation, stronger
debt management, and more capable state-asset supervision. These capacities
make it easier to classify platform obligations, place eligible projects into
formal fiscal instruments, reorganize assets and liabilities, and monitor the
boundary between commercial operations and government financing. Historical
state capacity should therefore shape the type of exit a locality can achieve.

The measurement contribution is equally important. The paper develops a
city-platform coding strategy that separates source-only candidates from final
human-validated labels. This distinction is necessary because the documentary
record is uneven. Some cases contain clean official exit statements but limited
evidence about post-exit functions; others contain rich evidence about
continuing platform activity but no direct formal-exit document. Treating both
as measured outcomes would blur the distinction the paper measures.
The LLM-assisted coding procedure helps scale the review of heterogeneous
documents, but the final labels remain tied to original source evidence,
alternative labels, confidence levels, and human review.

The pilot evidence should be read in that spirit. The cases do not yet estimate
the effect of historical state capacity on LGFV exit types. They show
that the proposed categories can be applied to original documents and that the
same official reform language can correspond to different institutional
outcomes. Guangzhou illustrates a case closer to substantive exit because the
company shifted away from new government-project financing toward
fiscal-funded entrusted management. Xi'an, Chengdu, and Zhuzhou illustrate
nominal exit, where formal exit or no-government-financing language coexists
with continuing evidence of public-project and fiscal-support functions.
Hangzhou illustrates functional transfer through the consolidation of public
project and debt functions inside a reorganized municipal platform system.

Two limitations follow directly from the design. First, the pilot sample is a
measurement exercise rather than a representative sample. The next empirical
step is to expand the city-platform sample while preserving the separation
between candidate cases and final labels. Second, the historical-capacity
argument requires a design that compares exit types across a broader set of
cities after accounting for contemporary fiscal pressure, economic development,
land finance dependence, and debt burden. These limitations are not separate
from the paper's contribution. They define the conditions under which a
stronger empirical analysis can be built without collapsing substantive exit,
nominal exit, functional transfer, and liquidation back into a single measure
of official compliance.
