\section{Empirical Strategy}

The baseline empirical analysis estimates whether historical state capacity
predicts the probability of substantive exit. A simple specification is:

\begin{equation}
SubstantiveExit_i = \alpha + \beta HistoricalCapacity_i + X_i'\gamma + \epsilon_i,
\end{equation}

where $SubstantiveExit_i$ indicates whether city or platform $i$ achieved
substantive exit, $HistoricalCapacity_i$ measures historically rooted state
capacity, and $X_i$ includes contemporary fiscal, economic, debt, and political
controls.

The first version of $HistoricalCapacity_i$ will be constructed from CHGIS. The
main measure is Qing administrative density: the number of late-imperial county
or prefectural administrative units intersecting the contemporary
prefecture-level city, scaled by land area. This measure captures the depth of
historical administrative presence rather than contemporary fiscal strength.
The main alternative measure will use CBDB to construct Ming-Qing elite density,
especially the density of high-degree civil service examination holders by
place of affiliation. This second measure captures local administrative human
capital and elite formation. A third measure, based on Ming courier routes and
stations, can be used as a robustness check for historical communication and
transport infrastructure.

A second specification uses exit type as a multinomial outcome:

\begin{equation}
Pr(ExitType_i = k) = f(HistoricalCapacity_i, X_i),
\end{equation}

where $k$ indexes substantive exit, nominal exit, functional transfer, and
liquidation. This model directly evaluates whether historical state capacity is
associated with different institutional responses to the same central reform.

Mechanism tests examine whether stronger historical state capacity is associated
with greater formal fiscal substitution after exit. Relevant outcomes include
special-purpose bond use, on-budget infrastructure spending, project pipeline
readiness, debt restructuring capacity, and changes in non-platform local SOE
debt. These outcomes are not the main dependent variables of the paper; instead,
they help explain why some localities are able to achieve substantive exit while
others rely on adaptive workarounds.
