\section{Introduction}

China's local government financing vehicle (LGFV) exit reform poses a
measurement problem before it poses an explanation problem. Official reports
describe large reductions in the number of platform companies and the volume of
their operational financial debt. These figures suggest progress in local debt
management, but they do not reveal whether the underlying government financing
function has disappeared, moved elsewhere, or continued under a different
label. Official exit is not institutional exit.

This paper develops a measurement framework for distinguishing formal
compliance from functional fiscal change. The core outcome is not whether a
platform is reported to have exited. It is the institutional fate of the fiscal
function that the platform previously performed. Some platforms achieve
\emph{substantive exit}: they genuinely stop performing government financing or
quasi-fiscal financing functions. Others display \emph{nominal exit}: formal
exit or no-government-financing language appears while the same platform
continues similar public investment, construction, land preparation, repayment,
or fiscal-support functions. Still others undergo \emph{functional transfer}:
the original platform exits, but its financing, construction, or debt
management role moves to another local state-owned or quasi-state entity. A
final category, \emph{liquidation}, captures cases in which the firm
disappears through deregistration, bankruptcy, liquidation, or another form of
termination.

The distinction matters because LGFVs have long occupied the space between
formal budgets and local development mandates. They allowed local governments
to finance infrastructure, land development, industrial parks, urban
construction, and other quasi-public projects outside the ordinary budget
\citep{oi1992,oi1995,wong2013,tsui2011}. They also helped local governments
manage a persistent fiscal tension: local governments carry extensive
expenditure responsibilities, but they have faced tight formal constraints on
ordinary borrowing \citep{montinola1995,jin2005}. When land revenues declined
and repayment risks increased, platform finance became a central target of
debt regulation \citep{tsui2011,bai2016longshadow}. Yet regulatory success
cannot be read directly from official exit counts. A reduction in platform
numbers can reflect genuine fiscal formalization, relabeling, reorganization,
or disappearance.

The paper therefore asks two linked questions. How should LGFV exit be
measured when the relevant outcome is embedded in administrative, financial,
and corporate documents rather than in a single official register? Once exit
is measured as institutional fate, why are some localities more able than
others to convert official exit into substantive functional change? The first
question is the paper's main contribution. The second provides the explanatory
argument that makes the measurement substantively useful.

I argue that LGFV exit should be coded through the post-exit location of the
government financing function. This requires evidence on both sides of the
event: the formal exit or compliance statement, and the continued or
discontinued performance of fiscal functions after that event. The coding rule
therefore treats official no-government-financing language as evidence, but
not as the outcome itself. It asks whether the same issuer, a related local
SOE, or a reorganized platform group continues to carry public project
financing, entrusted construction, land preparation, fiscal repayment,
government purchase service, or comparable quasi-fiscal functions.

The explanatory argument is that historically rooted state capacity shapes the
institutional fate of exit. LGFV exit is not simply a regulatory instruction
to remove a label. It requires local governments to replace functions
previously performed by platforms through formal fiscal instruments, budgetary
channels, regulated state assets, or genuinely commercial operations. That
substitution depends on fiscal absorption, bureaucratic coordination, and
project and state-asset governance. These capacities allow local officials to
classify platform obligations, move eligible public investment into regulated
fiscal channels, coordinate asset and debt reorganization, and monitor whether
post-exit firms recreate hidden debt through entrusted construction,
repurchase agreements, subsidiaries, or fiscal subsidies.

Localities with stronger historically rooted administrative and fiscal
capacity should be more able to make this substitution. In these localities,
official exit is more likely to become substantive exit, or at least a
regulated reorganization of former platform functions. Localities with weaker
capacity should be more likely to preserve the old function through nominal
compliance or functional transfer. State capacity is therefore not the object
being measured. It is an explanation for why the same official reform can
produce different institutional fates.

Empirically, the paper develops a case-level coding strategy. The unit of
analysis is a city-platform case, and each label records both the formal exit
event and the post-event location of the relevant function. The evidence comes
from government announcements, finance-bureau and state-owned asset supervision
documents, company disclosures, bond prospectuses, credit rating reports,
legal opinions, annual reports, business registration records, and credible
financial news. Large language models generate preliminary labels under a
fixed codebook, but final labels are assigned only after human review of the
original documents.

The current label file contains sixty-eight human-validated city-platform
cases and a seed pool of 257 candidate disclosures for LLM-assisted screening.
The validated labels already recover three distinct institutional outcomes.
Guangzhou and Ningbo are coded as substantive exit. Hangzhou, Wenzhou, Foshan,
and several reorganized platform cases are coded as functional transfer. Most
validated cases are nominal exits, including transport, development-zone,
cultural-tourism, county-level, and district platforms where
no-government-financing language coexists with continuing public project
functions. A small descriptive comparison links the sixty-two historically
matched labels to historical-capacity bins. It is not yet a population
estimate, but it shows that the coding scheme recovers institutional variation
and that the pilot already contains useful comparisons between high-capacity
substantive cases and lower-capacity nominal cases.

The paper's main contribution is a measurement framework for studying
compliance reforms whose visible administrative label may diverge from the
underlying state function. For LGFV exit, this means disaggregating official
exit into substantive exit, nominal exit, functional transfer, and
liquidation. The framework makes it possible to ask whether debt regulation
changes fiscal institutions or merely changes the organizational form through
which fiscal functions are carried out. A second contribution is theoretical:
the paper links variation in exit fate to historically rooted state capacity,
understood as the local ability to absorb fiscal obligations, coordinate
bureaucratic and corporate reorganization, and govern public projects and state
assets. A third contribution is methodological. The paper develops an
auditable LLM-assisted, human-validated coding protocol for heterogeneous
documents, treating machine labels as provisional measurement inputs rather
than final outcomes.

The rest of the paper proceeds as follows. The next section positions the
paper in relation to work on Chinese fiscal decentralization, local debt, and
state capacity. The following section describes the background of LGFV
expansion and exit reform. The theory section develops the distinction between
official exit and institutional fate and explains why historical state
capacity should affect the probability of substantive exit. The subsequent
sections describe the research design, coding strategy, and empirical
strategy.
