\section{Literature and Contribution}

The paper builds on work in Chinese fiscal decentralization, local debt, and
state capacity. Existing studies show that China's local governments operated
under strong development incentives, broad expenditure responsibilities, and
constrained formal borrowing authority \citep{montinola1995,jin2005}. Under
these conditions, local officials used land finance, local state-owned
enterprises, and platform companies to sustain investment and urban expansion
\citep{oi1992,oi1995,wong2013}. This literature explains why quasi-fiscal
instruments became central to local development. It does not fully explain what
happens when the center later tries to unwind those instruments. The exit
reform therefore offers a useful setting for studying not only local adaptation
under decentralization, but also the political economy of recentralization and
fiscal formalization.

Research on China's post-2008 fiscal expansion shows how infrastructure
stimulus, land-centered growth, and local borrowing created durable debt
obligations and financial risk \citep{tsui2011,bai2016longshadow}. This work
treats LGFVs as important carriers of local fiscal stress. The present paper
builds on that insight but shifts the dependent variable. Rather than measuring
only the level of local debt, the volume of platform liabilities, or the
presence of an official exit event, it asks where the government financing
function goes after exit. This distinction matters because fiscal risk can be
reduced, relabeled, transferred, or temporarily hidden. A locality may appear
compliant in aggregate statistics while still relying on similar organizational
arrangements to finance public projects.

Work on state capacity emphasizes the administrative and fiscal institutions
that allow governments to tax, regulate, provide public goods, and make social
and economic activity legible to the state
\citep{besley2009,scott1998,dincecco2017}. Historical political economy further
shows that administrative density, elite formation, and center-local agency
problems can leave durable traces in later governance outcomes
\citep{sng2014,bai2016elite,johnson2017}. The paper uses this literature to
make a specific argument about contemporary Chinese fiscal reform. Historical
capacity should matter not because past institutions mechanically determine
present policy, but because they may shape the local administrative routines
and fiscal organizations through which contemporary officials implement central
mandates.

The paper contributes by linking these literatures through a new measurement
problem. Existing accounts often treat LGFV exit as a binary indicator: a
platform either exits or does not. This paper disaggregates exit into four
institutional types: substantive exit, nominal exit, functional transfer, and
liquidation. The classification makes it possible to distinguish formal
compliance from functional fiscal change. It also gives the historical state
capacity argument an observable implication. Stronger localities should be more
able to convert official exit into substantive exit because they can absorb
former platform functions into formal fiscal and budgetary channels. Weaker
localities should be more likely to preserve those functions through nominal
exit, restructuring, continued support, or transfer to other local state-owned
entities.
