\section{Pilot Evidence Appendix}

This appendix reports the case-level evidence behind the pilot empirical
section. The tables are intentionally detailed. The main text uses summary
patterns, while the appendix lets readers inspect how each label, historical
capacity match, and mechanism claim is supported by source material.

\subsection{Validated Labels}

Table \ref{tab:pilot-validated-labels} reports the human-validated labels in
the historically matched pilot subset. The table records the event basis for
each label, the final exit type, and the matched historical elite-density
measure. It is the case-level counterpart to the summary counts in the main
text.

\input{tables/pilot_validated_exit_types}

\subsection{Historical Capacity Matches}

Table \ref{tab:pilot-historical-capacity} reports the CBDB-GADM
historical-capacity match used in the pilot analysis. The table includes the
seventy-five historically matched validated cases and three candidate cases retained
for comparison or future source collection.

\input{tables/pilot_case_historical_capacity}

\subsection{Mechanism Evidence}

Table \ref{tab:pilot-mechanism-evidence} reports qualitative mechanism notes
for the historically matched validated cases. These notes are not treated as
separate quantitative outcomes in the pilot. Their role is to show whether the
documentary record contains evidence relevant to fiscal absorption,
bureaucratic coordination, and project or state-asset governance.

\input{tables/pilot_mechanism_evidence}

\subsection{Source Audit}

Table \ref{tab:pilot-source-audit} records the source trail behind the
historically matched pilot labels. The full human-validated label file now
contains eighty-five cases, and this table reports the seventy-five cases currently
matched to the CBDB-GADM historical-capacity crosswalk. For each case, it
lists the primary document used for the label, the formal exit or compliance event, the observed
post-event function, and the final coding decision. The table is deliberately
redundant with the case packets. Its purpose is to let readers see where the
coding judgment comes from before accepting the descriptive patterns in the
pilot section.

\input{tables/pilot_source_audit}
