\section{Research Design}

The previous sections argued that official LGFV exit is not a single
institutional outcome. I now describe the research design used to measure this
variation and to link it to historical state capacity. The unit of analysis is
a city-platform case rather than a city-year, and the labeled sample is built
from original documentary evidence rather than from aggregate counts of
financing vehicles or outstanding debt.

By a city-platform case, I mean a major LGFV or platform-like local
state-owned enterprise located within a prefecture-level city. This unit is
narrower than a city-level measure of exit, but it is better suited to the
main measurement problem in the paper. Official statistics can show whether a
locality reduced the number of financing vehicles or lowered the reported
stock of platform debt. They cannot show, by themselves, whether the public
financing, construction, project-management, and debt functions attached to a
specific platform disappeared, remained inside the same issuer, moved to
another state entity, or were absorbed into budgetary instruments. The
city-platform case makes this distinction observable because it follows the
organization before and after an exit, transformation, restructuring, or
liquidation event.

The dependent variable is LGFV exit type. I code each case into one of four
categories: substantive exit, nominal exit, functional transfer, or
liquidation. Substantive exit means that the platform no longer performs
government financing or quasi-fiscal financing functions after the relevant
event. Nominal exit means that formal exit language appears, but the same
platform continues to finance or implement public projects in ways that
preserve the government financing function. Functional transfer means that the
function moves to another local state-owned entity, merged group, subsidiary,
or newly established platform. Liquidation means that the original entity is
dissolved, deregistered, bankrupted, or otherwise terminated.

Sample construction begins with a source inventory for candidate city-platform
cases. The inventory draws on government documents, finance-bureau notices,
state-owned asset supervision records, bond prospectuses, credit rating
reports, legal opinions, annual reports, exchange disclosures, business
registration records, and credible financial news. A case enters the inventory
when there is evidence that the company was a platform or platform-like local
state-owned enterprise, or when it appears in documents connected to local debt
resolution, infrastructure investment, government-entrusted construction, or
platform transformation. I then separate source-only candidates from label
candidates. A source-only candidate has useful evidence about platform
functions but lacks a document identifying a formal exit,
no-government-financing statement, transformation, restructuring, or dissolution
event. A label candidate has both baseline platform evidence and post-event
evidence that can be evaluated under the coding rule developed in the next
section. Final labels are assigned only after human review of the original
source documents.
This separation keeps the sample from treating the most visible or best
documented cases as if they were already measured outcomes.

The first stage of the paper uses a pilot sample rather than a large
cross-sectional dataset. This choice is deliberate. The categories are useful
only if they can be applied consistently to original documents across cases
with different institutional patterns and source quality. The pilot therefore
prioritizes variation in city capacity, platform function, exit language, and
documentary form over representativeness. It is not intended to estimate the
main historical-capacity effect. Its purpose is to validate the measurement
scheme, identify ambiguous cases, and discipline the larger source-collection
process.

The current label file contains forty-one human-validated cases. Guangzhou
City Construction Investment Group and Ningbo Development Investment Group are
coded as substantive exit because the available disclosures show movement away
from off-budget government-project financing. Hangzhou City Investment Group,
Wenzhou Mingcheng Construction Investment Group, Foshan Construction
Development Group, and several reorganized platform cases are coded as
functional transfer because public project functions continue through
reorganized platform groups, guarantor structures, SASAC entrustment, state
capital channels, or fiscal-settlement contracts. Xi'an Hi-tech Holding,
Chengdu City Construction Investment Management Group, Zhuzhou State-owned
Assets Investment Holding Group, Xuzhou Xinsheng Investment Holding Group,
Hengyang City Construction Investment, Jinan City Investment Group, Yancheng
City Asset Investment Group, Suzhou City Construction Investment Group,
Huangshi Urban Development Investment Group, Yancheng Chengnan New District
Development and Construction Investment, Suzhou Xiangcheng City Construction
Investment Group, Linyi City Construction Investment Group, Ji'an City
Construction Investment Development, Luoyang Urban-Rural Construction
Investment Group, Zhangjiagang City Investment, Tianjin Jinnan City
Construction Investment, Lu'an City Construction Investment, and Taizhou City
Construction Investment Group are coded as nominal exit. In these
cases, formal exit or no-government-financing language coexists with continuing
evidence of infrastructure investment, entrusted construction, fiscal payment
arrangements, land preparation, major project construction, government-linked
repayment, or fiscal subsidies.

The pilot also contains candidate cases that are not yet final labels. This
distinction is important because weak-capacity localities often appear in the
documentary record through debt-resolution notices, bank-loan restructuring
announcements, rating attention notices, and evidence of continuing fiscal
support rather than through clean exit-list documents. Luzhou Xinglu is the
closest candidate case. Its source packets from 2015, 2017, 2018, 2021, and
2023 show infrastructure investment-financing, government-entrusted
construction, fiscal receivables, project repayment, and government support.
They also contain compliance language about post-2015 debt and
no-government-financing rules. The case remains outside the final labeled
sample because I have not yet found a direct platform-list exit or
debt-resolution source that names Xinglu or the Luzhou platform cluster. Zunyi
Daoqiao and Liupanshui Kaitou are treated similarly. Both have evidence of
continuing public-project and infrastructure-construction functions under
conditions of fiscal and debt pressure, but neither is assigned a final
exit-type label until the formal event is documented or the absence of such an
event is recorded systematically.

The main explanatory variable is historical state capacity. Candidate measures
include Qing county and prefecture density, distance to historical
administrative centers, imperial examination degree density, historical tax
capacity, historical transportation infrastructure, courier station density,
and other indicators of historical administrative penetration. The empirical
section begins with two operational measures that can be implemented with
available data: Qing administrative density from CHGIS and Ming-Qing elite
density from CBDB matched to contemporary prefecture-level cities. These
measures are not intended to capture contemporary wealth directly. They measure
historically rooted administrative presence and local administrative human
capital, which the theory links to contemporary fiscal substitution capacity.

Contemporary controls include GDP per capita, fiscal self-sufficiency, local
debt burden, land finance dependence, industrial structure, population size,
marketization, and political tenure. These variables address a simple
alternative explanation: stronger contemporary economies may be better able to
exit LGFVs regardless of historical state capacity. The design therefore asks
whether historically rooted capacity predicts exit type after accounting for
current fiscal and economic conditions, and whether the association runs
through observable forms of formal fiscal substitution.
