\section{Theory}

The previous section introduced the distinction between official exit and exit
type. This section develops the theoretical argument. The central claim is that
LGFV exit requires more than formal compliance with a central directive. It
requires local governments to replace, reorganize, or discontinue functions that
platform companies previously performed. Because these tasks differ in their
administrative and fiscal requirements, local state capacity should affect the
type of exit that localities can achieve \citep{besley2009,dincecco2017}.

\subsection{Official and institutional exit}

I distinguish between \emph{official exit} and \emph{institutional exit}.
Official exit refers to a formal administrative or documentary status: a
platform company is removed from an official list, declared to have withdrawn
from government financing functions, or described as having completed
market-oriented transformation. Institutional exit refers to the substantive
change in the quasi-fiscal function previously performed by the platform. The
two concepts are related, but they are not identical. Official exit is observed
in documents and regulatory classifications. Institutional exit must be inferred
from the post-exit allocation of financing, construction, project management,
and debt rollover functions.

This distinction matters because LGFVs are not ordinary firms in local fiscal
politics. They are organizational devices through which local governments have
financed projects, managed development obligations, and connected land,
infrastructure, credit, and state assets \citep{wong2013,tsui2011}. A reform
that changes the legal or administrative status of the platform may or may not
change this fiscal role. If the platform no longer borrows for the government
and former projects are absorbed by formal fiscal instruments, official exit
corresponds to institutional exit. If the platform remains responsible for
public projects or if the same function is transferred to another local
state-owned entity, official exit changes the organizational label without
eliminating the underlying function.

\subsection{Exit types}

The paper classifies LGFV exit into four types. This classification is designed
to capture the post-exit location of the government financing function rather
than the language used in official announcements.

First, substantive exit occurs when the platform genuinely ceases to perform
government financing or quasi-fiscal functions. In this case, the company may
continue to exist as a market-oriented firm, but it no longer acts as an
off-budget fiscal arm of the local government. Evidence for substantive exit
includes a decline in public project financing, a reduction in fiscal support
arrangements, a shift toward commercial revenue, and the absorption of former
platform functions by formal budgetary instruments.

Second, nominal exit occurs when the company is officially removed from a list
or declared transformed but continues to perform similar functions. The
observable form changes, but the substantive relationship between the firm and
the local government remains similar. This category is likely when post-exit
documents continue to describe infrastructure construction, land development,
public welfare projects, fiscal subsidies, asset injections, or repayment
support from the local state.

Third, functional transfer occurs when the original platform exits but its
financing or project function moves to another local state-owned enterprise,
subsidiary, merged entity, newly established group company, or quasi-state
organization. Unlike nominal exit, the continuing function is not necessarily
located in the same firm. The relevant evidence lies in reorganizations, asset
transfers, new debt issuers, new project companies, or changes in the identity
of the local entity that carries out infrastructure and financing tasks.

Fourth, liquidation occurs when the company is dissolved, deregistered,
bankrupted, or otherwise ceases operations. Liquidation is conceptually
distinct from substantive exit because it describes the disappearance of the
organizational entity, not necessarily the formal absorption of its function by
the budget. In some cases, liquidation may follow from a genuine end of the
platform's fiscal role. In other cases, it may coexist with functional transfer
if another local entity assumes the same responsibilities.

\subsection{Formal fiscal substitution}

The key mechanism is \emph{formal fiscal substitution}. By formal fiscal
substitution, I mean the process through which a local government replaces
platform-based quasi-fiscal financing with formal fiscal instruments, regulated
state asset management, or genuinely commercial operations. The mechanism has
four components. First, local governments must classify existing platform
projects and decide which obligations are public, which are commercial, and
which are no longer viable. Second, they must move eligible public projects into
special-purpose bonds, budgetary expenditure, or other regulated fiscal
channels. Third, they must reorganize the assets, liabilities, and project
obligations attached to platform companies. Fourth, they must monitor the
boundary between commercial operations and government financing after the
formal exit event.

Each component requires administrative capacity. Project classification requires
information about repayment sources, land revenue expectations, construction
progress, and contractual obligations. Special-purpose bond substitution
requires eligible projects, expected revenue streams, documentation, and
compliance with central rules. Budgetary absorption requires fiscal planning,
expenditure discipline, and the ability to carry infrastructure spending on the
formal budget. Asset and liability reorganization requires coordination among
finance bureaus, state-owned asset supervisors, creditors, rating agencies, and
platform companies. Post-exit monitoring requires local officials to keep a
platform from recreating implicit government borrowing through subsidiaries,
entrusted construction, project repurchase, or fiscal subsidy arrangements.

In this sense, LGFV exit is a problem of fiscal legibility as well as debt
management. Local governments must make previously quasi-formal obligations
visible, classifiable, and governable through formal institutions
\citep{scott1998,besley2009}. Substantive exit is therefore not simply a choice
to comply with central rules. It is an institutional outcome that depends on
whether the local state can replace an informal fiscal instrument with formal
channels that still finance public investment and manage existing debt.

Nominal exit and functional transfer arise when formal fiscal substitution is
incomplete. If local officials face pressure to meet central targets but cannot
move projects and liabilities into formal channels, they may preserve the
function inside the same company while changing its official status. If
regulatory pressure is directed at a specific platform company or a platform
list, they may move the function to another local state-owned entity. In both
cases, the locality can display formal compliance while continuing to rely on
quasi-fiscal arrangements for development and debt management.

\subsection{Historical state capacity}

Historical state capacity refers to durable local administrative and fiscal
capacity formed through long-run processes of state building. In the Chinese
context, candidate indicators include administrative density, proximity to
historical administrative centers, imperial examination density, historical tax
capacity, transportation access, and other measures of the historical reach of
the state into local society \citep{sng2014,bai2016elite}. These measures do
not imply that Qing-era institutions mechanically determine contemporary fiscal
behavior. The claim is more modest: historically stronger localities may have
developed administrative routines, fiscal practices, elite-state linkages, and
organizational resources that persist, in altered form, into contemporary
governance \citep{dincecco2017,johnson2017}.

The connection between historical capacity and LGFV exit operates through
contemporary administrative and fiscal capacity. The argument has three steps.
First, historically stronger localities should be more likely to have finance
bureaus, development and reform agencies, and state asset supervisors with
greater experience in project preparation, budget management, and debt
monitoring. Second, these administrative resources should make formal fiscal
substitution more feasible, because the locality can identify eligible
projects, prepare special-purpose bond documentation, absorb some obligations
into budgetary channels, and restructure platform assets without losing control
over public investment. Third, where substitution is feasible, official exit is
more likely to become substantive exit rather than nominal exit or functional
transfer.

Historically weaker localities face a different problem. They may have relied
more heavily on flexible organizational devices because formal fiscal resources
and administrative routines are insufficient for the tasks assigned to local
governments. When the central government restricts LGFV financing, these
localities still need to maintain infrastructure investment, service existing
debts, and carry out development projects. If formal instruments do not provide
enough capacity to replace the platform, local officials have stronger
incentives to preserve the function through nominal exit or functional
transfer. The observed exit type should therefore reflect not only willingness
to comply, but also the local capacity to substitute formal fiscal institutions
for platform-based finance.

\subsection{Hypotheses}

The argument generates three hypotheses. First, cities with stronger historical
state capacity should be more likely to achieve substantive LGFV exit. This
does not mean that they face less fiscal pressure, but rather that they have
greater administrative and fiscal capacity to move former platform functions
into formal channels.

\paragraph{H1.} Higher historical state capacity is associated with a higher
probability of substantive LGFV exit.

Second, cities with weaker historical state capacity should be more likely to
display nominal exit or functional transfer. In these places, official exit can
serve as a response to central pressure while the underlying financing function
continues inside the same firm or another local state-owned entity.

\paragraph{H2.} Lower historical state capacity is associated with a higher
probability of nominal exit or functional transfer.

Third, the relationship between historical state capacity and exit type should
operate through contemporary fiscal substitution capacity. Cities with stronger
historical capacity should display greater use of formal instruments such as
special-purpose bonds, stronger budgetary absorption of infrastructure
spending, better project preparation, more capable state asset reorganization,
and less evidence of new quasi-fiscal debt accumulation outside the original
platform sector.

\paragraph{H3.} The association between historical state capacity and
substantive exit is mediated by contemporary fiscal substitution capacity.
