\documentclass[12pt]{article}

\usepackage[margin=1in]{geometry}
\usepackage{amsmath}
\usepackage{natbib}
\usepackage{hyperref}
\usepackage{array}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{graphicx}
\usepackage{xcolor}

\linespread{1.3}

\title{Beyond Official Exit: State Capacity and the Institutional Fate of China's LGFVs}
\author{Shunyu Hao}
\date{\today}

\begin{document}

\maketitle

\begin{abstract}
China's local government financing vehicle (LGFV) exit reform is often measured
through official reductions in platform counts or reported financing debt. Yet
official exit does not necessarily indicate functional fiscal change. A
platform may stop performing quasi-fiscal financing, continue the same function
under compliant language, transfer the function to another local state-owned
entity, or disappear through liquidation. This paper develops a measurement
framework for distinguishing formal compliance from functional fiscal change.
It codes LGFV exit as an institutional fate: substantive exit, nominal exit,
functional transfer, or liquidation. I then use this framework to study why
some localities can turn official exit into substantive institutional change
while others preserve platform functions through nominal or transferred forms.
The argument is that historically rooted state capacity affects the local
ability to absorb fiscal functions, coordinate bureaucratic reorganization, and
govern projects and state assets after exit. The paper introduces an
LLM-assisted, human-validated coding protocol using government documents,
company disclosures, bond prospectuses, credit rating reports, legal opinions,
and business registration records. The current label file contains
eighty-seven human-validated cases and is paired with a seed pool of 303
candidate disclosures for LLM-assisted screening. The expanded screening file
contains 131 LLM surrogate exit-type labels. The validated cases show that
identical official compliance language can correspond to distinct
institutional outcomes.
\end{abstract}

\input{sections/introduction}
\input{sections/literature}
\input{sections/background}
\input{sections/theory}
\input{sections/research_design}
\input{sections/coding_strategy}
\input{sections/empirical_strategy}
\input{sections/conclusion}

\appendix
\input{sections/pilot_appendix}
\clearpage

\bibliographystyle{plainnat}
\bibliography{references}

\end{document}
